Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-07-31 ms.tex
Update on Overleaf.

\section{Introduction} \label{sec:intro}
Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars. This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). \textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback. However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe. But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars. The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.][]{Hu2017,Peters2017}. However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}

@@

%\textbf{Stellar Ionizing Radiation Models} $-$
In our fiducial simulation, we follow photoionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}. This method places and evolves 48 rays on a HEALPix grid around each emitting source star for both HI and HeI ionizing radiation. Rays are adaptively split as they propagate away from their source to increase the angular resolution such that the solid angle of the ray remains smaller than 1/3 of the cell area. Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).

>>>>

\section{Introduction} \label{sec:intro}
Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars. This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews). \textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback. However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe. But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars. The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Hu2018}. However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}

@@

%\textbf{Stellar Ionizing Radiation Models} $-$
In our fiducial simulation, we follow photoionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}. This method places and evolves 48 rays on a HEALPix grid around each emitting source star for both HI and HeI ionizing radiation. Rays are adaptively split as they propagate away from their source to increase the angular resolution such that the solid angle of the ray remains smaller than 1/3 of the cell area. Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays). \textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work \citet[see][]{WiseAbel2012}.}
